<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-02-16 figures_01312022.Rmd
switch branch test

write.csv(PK.fit.table.1comp[[1]] <- "inst/ext/PK.fit.table.1comp.DATE.csv")
write.csv(PK.fit.table.1comp[[2]] <- "inst/ext/processed.1comp.data.DATE.csv")

write.csv(PK.fit.table.2comp[[1]] <- "inst/ext/PK.fit.table.1comp.DATE.csv")
write.csv(PK.fit.table.2comp[[2]] <- "inst/ext/processed.1comp.data.DATE.csv")
```

@@

### read in PK output files
pk_output_1comp_12212021 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv")
pk_output_2comp_12212021 <- read.csv("inst/ext/PK.fit.table.2comp.12212021.csv")

### read in processed raw data files
raw_1comp_12212021 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
raw_2comp_12212021 <- read.csv("inst/ext/processed.2comp.data.12212021.csv")

@@

### save data
save(pk_output_1comp_12212021, file = "figures_rdata/pk_output_1comp_12212021.Rdata")
save(pk_output_2comp_12212021, file = "figures_rdata/pk_output_2comp_12212021.Rdata")
save(raw_1comp_12212021, file = "figures_rdata/raw_1comp_12212021.Rdata")
save(raw_2comp_12212021, file = "figures_rdata/raw_2comp_12212021.Rdata")
save(pk_lombardo, file = "figures_rdata/pk_lombardo_02072022.Rdata")

### save cp data
save(cp_df, file = "figures_rdata/cp_df.Rdata")
```

@@

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data2 <- pk_output_2comp_12212021 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data2 <- dplyr::select(raw_2comp_12212021, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs",
                                                  "V1",
                                                  "Ralphatokelim",
                                                  "Fbetaofalpha"))

@@

@@

@@

data2 <- pk_output_2comp_12212021 %>%
  filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")

@@

p <- ggplot(data = data,
            mapping = aes(x = sigma_value)) +
  geom_histogram(bins = 15) +
  # geom_density() +
  # scale_y_log10()+
  scale_x_log10() +
  theme_bw() +
  labs(x = "Sigma",
       y = "Number of observations") +
  facet_wrap(.~ model)
# stat_function(fun = dlnorm, args = list(mean = mean(log(data$sigma_value)), sd = sd(log(data$sigma_value))))

@@

data2 <- as.data.table(pk_output_2comp_12212021 %>%
                         filter(param.value.type == "Fitted geometric mean"))

@@

raw_data2 <- raw_2comp_12212021

pk_data2 <- pk_output_2comp_12212021 %>% 
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

@@

pk_data2 <- pk_output_2comp_12212021

@@

pk_data1 <- as.data.table(pk_output_1comp_12212021)
pk_data2 <- as.data.table(pk_output_2comp_12212021)

@@

  pk_all <- pk_all %>%
    filter(status == "bad fit") %>% ### only want bad fit
    mutate(status = NULL) %>% ### get rid of status column
    group_by(Compound) %>%  
    filter(n() == 2) %>% ### group_by compound and only keep compounds with two observations, aka neither model worked
    mutate(model = NULL) %>% ### get ride of model column
    distinct() ### discard repeated compound names

@@

```{r}

>>>>

write.csv(PK.fit.table.1comp[[1]], "inst/ext/PK.fit.table.1comp.DATE.csv", row.names = FALSE)
write.csv(PK.fit.table.1comp[[2]], "inst/ext/processed.1comp.data.DATE.csv", row.names = FALSE)

write.csv(PK.fit.table.2comp[[1]], "inst/ext/PK.fit.table.2comp.02102022.csv", row.names = FALSE)
write.csv(PK.fit.table.2comp[[2]], "inst/ext/processed.2comp.data.02102022.csv", row.names = FALSE)
```

@@

### read in PK output files
pk_output_1comp_12212021 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv")
pk_output_2comp_02102022 <- read.csv("inst/ext/PK.fit.table.2comp.02102022.csv")
pk_output_flat_02102022 <- read.csv("inst/ext/PK.fit.table.flat.02102022.csv")

### read in processed raw data files
raw_1comp_12212021 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
raw_2comp_02102022 <- read.csv("inst/ext/processed.2comp.data.02102022.csv")
raw_flat_02102022 <- read.csv("inst/ext/processed.flat.data.02102022.csv")

@@

### save data
save(pk_output_1comp_12212021, file = "figures_rdata/pk_output_1comp_12212021.Rdata")
save(pk_output_2comp_02102022, file = "figures_rdata/pk_output_2comp_12212021.Rdata")
save(pk_output_flat_02102022, file = "figures_rdata/pk_output_flat_02102022.Rdata")
save(raw_1comp_12212021, file = "figures_rdata/raw_1comp_12212021.Rdata")
save(raw_2comp_02102022, file = "figures_rdata/raw_2comp_12212021.Rdata")
save(raw_flat_02102022, file = "figures_rdata/raw_flat_02102022.Rdata")
save(pk_lombardo, file = "figures_rdata/pk_lombardo_02072022.Rdata")

### save cp data
# save(cp_df, file = "figures_rdata/cp_df.Rdata")
```

@@

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data2 <- pk_output_2comp_02102022 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data2 <- dplyr::select(raw_2comp_02102022, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs",
                                                  "V1",
                                                  "Ralphatokelim",
                                                  "Fbetaofalpha"))

@@

cp_df$cp_pred_error <- (cp_df$cp - cp_df$Value) / cp_df$Value

cp_df <- cp_df %>% group_by(Species.x, 
                            Compound,
                            CAS,
                            type) %>%
  mutate(cp_pred_error_range = max(cp_pred_error, na.rm = TRUE) - min(cp_pred_error, na.rm = TRUE))

@@

```{r, make_cp_error_histogram}

data <- data %>%
  filter(cp != 1e-20)

data <- data %>%
  distinct(Species.x, Compound, CAS, cp_pred_error_range)

p <- ggplot(data = data,
            mapping = aes(x = cp_pred_error_range)) +
  geom_histogram() +
  scale_x_log10() +
  facet_wrap(. ~type)

```{r, make_cp_error_versus_dose}

data <- data %>%
  filter(type == "1-Compartment")

data <- data %>%
  group_by(Compound, CAS, Dose) %>%
  mutate(average = mean(cp_pred_error))

p <- ggplot(data = data, mapping = aes(x = Dose, y = average)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10()

@@

data2 <- pk_output_2comp_02102022 %>%
  filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")

@@

p <- ggplot(data = data,
            mapping = aes(x = sigma_value)) +
  geom_histogram(bins = 15) +
  # geom_density() +
  # scale_y_log10()+
  scale_x_log10() +
  theme_bw() +
  labs(x = "Sigma",
       y = "Number of observations") +
  facet_wrap(.~ model) +
  geom_vline(xintercept = 2.22e-06)
# stat_function(fun = dlnorm, args = list(mean = mean(log(data$sigma_value)), sd = sd(log(data$sigma_value))))

@@

data2 <- as.data.table(pk_output_2comp_02102022 %>%
                         filter(param.value.type == "Fitted geometric mean"))

@@

raw_data2 <- raw_2comp_02102022

pk_data2 <- pk_output_2comp_02102022 %>% 
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

@@

pk_data2 <- pk_output_2comp_02102022

@@

pk_data1 <- as.data.table(pk_output_1comp_12212021)
pk_data2 <- as.data.table(pk_output_2comp_02102022)

@@

pk_all <- pk_all %>%
  filter(status == "bad fit") %>% ### only want bad fit
  mutate(status = NULL) %>% ### get rid of status column
  group_by(Compound) %>%  
  filter(n() == 2) %>% ### group_by compound and only keep compounds with two observations, aka neither model worked
  mutate(model = NULL) %>% ### get rid of model column
  distinct() ### discard repeated compound names

@@

```{r, compare_AIC}

pk_data2 <- pk_output_2comp_02102022

pk_data_flat <- pk_output_flat_02102022 %>%
  filter(param.value.type == "Predicted" | param.value.type == "Fitted geometric mean" | param.value.type == "Fitted geometric std dev")

### make both data.frames have the same column names so they are rbind-able
pk_data1 <- pk_data1[, intersect(intersect(colnames(pk_data2), colnames(pk_data_flat)), colnames(pk_data1))]
pk_data2 <- pk_data2[, intersect(intersect(colnames(pk_data1), colnames(pk_data_flat)), colnames(pk_data2))]
pk_data_flat <- pk_data_flat[, intersect(intersect(colnames(pk_data1), colnames(pk_data2)), colnames(pk_data_flat))]

pk_data1 <- pk_data1 %>%
  rename(LogLikelihood_1 = LogLikelihood,
         AIC_1 = AIC,
         sigma_value_1 = sigma_value) %>%
  mutate(model = NULL) %>%
  mutate(model.type = NULL)

pk_data2 <- pk_data2 %>%
  rename(LogLikelihood_2 = LogLikelihood,
         AIC_2 = AIC,
         sigma_value_2 = sigma_value) %>%
  mutate(model = NULL) %>%
  mutate(model.type = NULL)

pk_data_flat <- pk_data_flat %>%
  rename(LogLikelihood_flat = LogLikelihood,
         AIC_flat = AIC,
         sigma_value_flat = sigma_value) %>%
  mutate(model = NULL) %>%
  mutate(model.type = NULL)

pk_all <- left_join(pk_data1, pk_data2, by = c("CAS",
                                              "Species",
                                              "param.value.type",
                                              "sigma_id",
                                              "Reference",
                                              "Data.Analyzed",
                                              "Compound"))

pk_all <- left_join(pk_all, pk_data_flat, by = c("CAS",
                                              "Species",
                                              "param.value.type",
                                              "sigma_id",
                                              "Reference",
                                              "Data.Analyzed",
                                              "Compound"))

pk_all <- subset(pk_all, select = c(CAS, Species, Compound, Reference, AIC_1, AIC_2, AIC_flat))

pk_all <- distinct(pk_all)

pk_all$AIC_1[pk_all$AIC_1 == Inf] <- NA
pk_all$AIC_2[pk_all$AIC_2 == Inf] <- NA
pk_all$AIC_flat[pk_all$AIC_flat == Inf] <- NA

pk_all <- pk_all %>%
  mutate(flat_lowest = ifelse(AIC_flat < AIC_1 & AIC_flat < AIC_2, 1, 0)) %>%
  mutate(flat_better_than_1 = ifelse(AIC_flat < AIC_1 & AIC_flat > AIC_2, 1, 0)) %>%
  mutate(flat_better_than_2 = ifelse(AIC_flat > AIC_1 & AIC_flat < AIC_2, 1, 0))

pk_just_bad <- pk_all %>%
  filter(flat_lowest == 1 | flat_better_than_1 == 1 | flat_better_than_2)
```

```{r, lombardo_comparisons}
